Formal Verification of Forward Secrecy and Post-Compromise Security for TreeKEM

### 2024-10-13 manuscript/manuscript-SBMF.tex
FFinishing touches

\begin{document}
%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
% [SS] Get rid of Spin in title (since this is not a FM conference). Add some umbrella term for FS/PCS to title? eg, Formal Verification of <blah> for TreeKEM and Continuous Group Key Agreement? 
%[AW] Good insight, how does the below sound?
\title{Formal Verification of Forward Secrecy and Post-Compromise Security for TreeKEM}
\titlerunning{TreeKEM: Verification of Forward Secrecy \& Post-Compromise Security}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%

@@

The final abstraction to be utilized in the modeling of TreeKEM protocol is the observation that, in its currently simplified form, the model can be viewed as a Markov Process
% [SSC] I think this is too common knowledge to need a cite (and save a few lines)
% [AWC] Agreed
%~\cite{markov1906a}.
Consider \Adversary entering a \CGKAsec state $s_{i}$.
How the TreeKEM protocol evolved prior to $s_{i}$ does not inform the moves available to \Adversary, rather the current game state $s_{i}$ solely informs this.
Furthermore, how the knowledge accumulated by \Adversary prior to $s_{i}$ was obtained does not further inform \Adversary of the TreeKEM protocol's CGKA key; instead all \Adversary knowledge is deduced from $s_{i}$.
Phrased differently, state $s_{i-1}$ has no unique information which informs state transitions from $s_{i}$, and state transitions from $s_{i}$ are determined solely from the information contained within $s_{i}$.

@@

The security guarantees under verification are encoded in \Abrev{LTL}.
\Abrev{LTL} expressions are natively supported by \Promela and Spin.
Below are the English definitions of \Abrev{FSU} and \Abrev{PCS} their corresponding \Abrev{LTL} formulae.

@@

The methodology presented is two-fold.
First, the performance is measured of the model \CGKAmodN{N} described in this work and compared with the performance of a precursor model defined by~\cite{washburn2022formal} 
denoted as \CGKAmodNT{N}{T}.
%[SSB] after "described" add "in sections 2.2-2.6"
The comparison model \CGKAmodNT{N}{T} is the same semantic encoding of \CGKAmodN{N} \emph{before} the abstractions described were applied, i.e:  $\Code{Abstractions}\Parens{\CGKAmodNT{N}{T}} =  \CGKAmodN{N}$.
Therefore \CGKAmodNT{N}{T} is an fitting comparative baseline from which the effects of the composed abstractions can be measured.
Comparison of performance is made across several metrics, including state-vector length, runtime, memory usage, state-space size, and transition count.
Both models performed verification of the \LTLPredicate{FSU} and \LTLPredicate{PCS} properties.
Second, \CGKAmodN{N} is utilized to verify \LTLPredicate{FSU} and \LTLPredicate{PCS} for parameters far beyond the capabilities of \CGKAmodNT{N}{T}.
Subsequently, the authors provide brief contextual commentary on these verification results.

>>>>

\begin{document}
%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
% [SS] Get rid of Spin in title (since this is not a FM conference). Add some umbrella term for FS/PCS to title? eg, Formal Verification of <blah> for TreeKEM and Continuous Group Key Agreement? 
%[AW] Good insight, how does the below sound?
\title{Formal Verification of Forward Secrecy and Post-Compromise Security for TreeKEM}
%%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%

@@

The final abstraction to be utilized in the modeling of TreeKEM protocol is the observation that, in its currently simplified form, the model can be viewed as a Markov Process.
% [SSC] I think this is too common knowledge to need a cite (and save a few lines)
% [AWC] Agreed
%~\cite{markov1906a}.
Consider \Adversary entering a \CGKAsec state $s_{i}$.
How the TreeKEM protocol evolved prior to $s_{i}$ does not inform the moves available to \Adversary, rather the current game state $s_{i}$ solely informs this.
Furthermore, how the knowledge accumulated by \Adversary prior to $s_{i}$ was obtained does not further inform \Adversary of the TreeKEM protocol's CGKA key; instead all \Adversary knowledge is deduced from $s_{i}$.
Phrased differently, state $s_{i-1}$ has no unique information which informs state transitions from $s_{i}$, and state transitions from $s_{i}$ are determined solely from the information contained within $s_{i}$.

@@

The security guarantees under verification are encoded in \Abrev{LTL}.
\Abrev{LTL} expressions are natively supported by \Promela and Spin.
Below are the English definitions of \Abrev{FSU} and \Abrev{PCS} with their corresponding \Abrev{LTL} formulae.

@@

The methodology presented is two-fold.
First, the performance is measured of the model \CGKAmodN{N} described in this work and compared with the performance of a precursor model defined by~\cite{washburn2022formal} 
denoted as \CGKAmodNT{N}{T}.
%[SSB] after "described" add "in sections 2.2-2.6"
The comparison model \CGKAmodNT{N}{T} is the same semantic encoding of \CGKAmodN{N} \emph{before} the abstractions described were applied, i.e:  $\Code{Abstractions}\Parens{\CGKAmodNT{N}{T}} =  \CGKAmodN{N}$.
Therefore \CGKAmodNT{N}{T} is a fitting comparative baseline from which the effects of the composed abstractions can be measured.
Comparison of performance is made across several metrics, including state-vector length, runtime, memory usage, state-space size, and transition count.
Both models performed verification of the \LTLPredicate{FSU} and \LTLPredicate{PCS} properties.
Second, \CGKAmodN{N} is utilized to verify \LTLPredicate{FSU} and \LTLPredicate{PCS} for parameters far beyond the capabilities of \CGKAmodNT{N}{T}.
Subsequently, the authors provide brief contextual commentary on these verification results.
